Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-04-03 ms.tex
almost done with edits to responses to co-authors

The final part is to perform the mock observation from the ideal
images produced in the previous step.  \edit{Both our HST- and
  LSST-like observations are monochromatic, respectively using the
  F606W and the g-band.} For HST-like observations, galaxies along the
line of sight already include noise and a point spread function (PSF).
We therefore stack and magnitude calibrate all components to produce
the final HST-like images, which are $300\times300~{\rm pix}^2$ with
$0.03$~arcsec per pixel.

@@

% Caveat of the mock data set
One major caveat to our resuls is the fact that our mock data likely
does not describe the full range of lens and non-lens images that will
be observed.  For example, the along the line of sight galaxies in our
training and test images all come from the Hubble Ultra Deep field,
sampling a smaller range of potential contaminants that are not
associated with a lensed image.  Also, the redshift of the source
galaxies have been fixed to $z_s=2$.  We will address these
shortcomings in subsequent work.

>>>>

The final part is to perform the mock observation from the ideal
images produced in the previous step.  \edit{Both our HST- and
  LSST-like observations are monochromatic, respectively using the
  F606W and the g-band.  We stack the lens galaxy, source image, and
  galaxies along the line of sight.  While we adjust the source size
  and magnitude to correspond to the change $D_s$ when placed at
  $z_s$, we do not adjust colors.  The distribution of lens properties
  is not realistic with a constant $z_s$, but provides a sufficient
  start in covering the feature space to test supervised
  classification methods.  Incorporating the lens, source image, line
  of sight galaxies, and noise are particularly crucial in methods
  that use edge features.}

For HST-like observations, \edit{the stacked component for galaxies
  along the line of sight already includes noise} and a point spread
function (PSF).  We therefore stack and magnitude calibrate all
components to produce the final HST-like images, which are
$300\times300~{\rm pix}^2$ with $0.03$~arcsec per pixel.

@@

% Caveat of the mock data set
One major caveat to our resuls is the fact that our mock data likely
does not describe the full range of lens and non-lens images that will
be observed.  For example, the along the line of sight galaxies in our
training and test images all come from the Hubble Ultra Deep field,
sampling a smaller range of potential contaminants that are not
associated with a lensed image.  \edit{A limitation of the
  CANDELS sources is that the sources are observed with HST seeing,
  and would not resolve the clumpiness within a true HST arc.}  Also,
the redshift of the source galaxies have been fixed to $z_s=2$.  We
will address these shortcomings in subsequent work.
